%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% See "README.md" for instructions on compiling this document.
% \usepackage{multicol}
\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
    % Class options:
    % a4paper, letterpaper, nonstopmode, draftmode
    % MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% PREAMBLE.
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    % CV Info (to be customized).
    \newcommand{\CVAuthor}{Xiaoting Fu}
    \newcommand{\CVTitle}
    {Specialized in Spoken Language Processing (SLP) with Machine Learning. 
    Looking for SLP/NLP or SE related internship.}
    % PDF settings and properties.
    \hypersetup{
    pdftitle={\CVTitle},
    pdfauthor={\CVAuthor},
    pdfsubject={\CVWebpage},
    pdfcreator={XeLaTeX},
    pdfproducer={},
    pdfkeywords={},
    unicode=true,
    bookmarks=true,
    bookmarksopen=true,
    pdfstartview=FitH,
    pdfpagelayout=OneColumn,
    pdfpagemode=UseOutlines,
    hidelinks,
    breaklinks}
    
    % Shorthand.
    \newcommand{\Code}[1]{\mbox{\textbf{#1}}}
    \newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% ACTUAL DOCUMENT.
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \begin{document}
    
    %%%%%%%%%%%%%%%
    % TITLE BLOCK %
    %%%%%%%%%%%%%%%
    
    \Title{\CVAuthor}
    
    \begin{SubTitle}
    {3133A Kings Ct, Raleigh, NC, 27606}
    \par
    \href{mailto:xfu7@ncsu.edu}
    {xfu7@ncsu.edu}
    \,\SubBulletSymbol\,
    +1\,(919)\,884-0552
    \
    \end{SubTitle}
    
    \begin{Body}
    %%%%%%%%%%%%
    %% OBJECTIVES&SUMMARY %%
    %%%%%%%%%%%%
    
    \Section
    {Objectives}
    {Objectives}
    {PDF:Objectives}
    
    \Entry
    \BulletItem
    Specialized in Spoken Language Processing (SLP) and Machine Learning. 
    \BulletItem
    Looking for SLP/NLP or SE related internship positions.
    %%%%%%%%%%%%%%%
    %% EDUCATION %%
    %%%%%%%%%%%%%%%
    
    \Section
    {Education}
    {Education}
    {PDF:Education}
    
    \Entry
    \href{http://www.ncsu.edu}
    {\textbf{Ph.D. in \href{https://www.csc.ncsu.edu/}
    {Computer Science}: North Carolina State University (NCSU)}}, Raleigh, NC
    \hfill
    \DatestampYM{2017}{08} --
    Present
    %\Gap
    \BulletItem
    Cumulative GPA: 3.7 / 4.0, Expected Graduation: \DatestampYM{2021}{05}
    \BigGap
    
    \Entry
    \href{http://www.wku.edu.cn}
    {\textbf{B.S. in
    \href{http://www.cs.wku.edu.cn}
    {Computer Science}: Wenzhou-Kean University (WKU)}}, Zhejiang, China
    \hfill
    \DatestampYMD{2013}{09}{01} --
    \DatestampYMD{2017}{06}{01}
    
    %\Gap
    \BulletItem
    Cumulative GPA: 3.9 / 4.0 (Graduated with College Honors)
    
    %%%%%%%%%%%%
    %% SKILLS %%
    %%%%%%%%%%%%
    
    \Section
    {Skills and Interests}
    {Skills and Interests}
    {PDF:Skills}
    
    \Entry
    \textbf{Languages:} Python, Shell, Java, CSharp, SQL \hfill  \textbf{Speech Recognition:} Kaldi, CMU Sphinx, DeepSpeech
    
    \textbf{Gesture Recognition:} Kinect, Leap Motion \hfill \textbf{OS \& Container:}  Unix OS, Windows, Docker
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% PROFESSIONAL EXPERIENCE %%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \Section
    {Professional Experience}
    {Professional Experience}
    {PDF:ProfessionalExperience}
    
    \Entry
    {\textbf{Software Engineer Intern | ABB | Raleigh, NC}}
    \hfill
    \DatestampYM{2018}{05} --
    \DatestampYM{2018}{08}
    \BulletItem
    Worked on ABB GridView Project. 
    Aimed at 1) providing an user interface for database interaction
    2) visualizing abstract energy marketing data and generate 3) 
    \BulletItem
    My contributions include: 
    1) developed tools to convert between different format of databases (SQLite and MS Access DB). 
    2) programmed tools for database comparison, changes review and apply changes from one database to another one.
    3) designed visual interfaces for the SQLite database editing. 
    4) implemented a SQL Parser for generating SQL action queries based on composite display queries.
    
    %%%%%%%%%%%%%%%%%%%%%%%%%
    %% PROJECTS %%
    %%%%%%%%%%%%%%%%%%%%%%%%%
    \Section
    {Selected Projects}
    {Selected Projects}
    {PDF:Projects}
    
    \Entry
    \textbf{FLECKS Project | ArgLab, NCSU | Raleigh, NC} \hfill Jan 2018 - Present
    \begin{Detail}
        \Entry
        \textbf{Intelligent Agent Prototyping}
        \BulletItem
        Aimed at developing a virtual learning companion for kids learning computer programming.
        \BulletItem
        My contributions include: 
        1) deployed the RHEL server for web hosting with Docker Container.
        2) coded the website to stream audio using Socket.io.
        3) integrated the Kaldi toolkit as a web service.
        
        \Entry
        \textbf{Continueous Speech Recognition for Children}
        \BulletItem
        Aimed at building an Automatic Speech Recognition (ASR) engine to recognize continuous children speech.
        \BulletItem
        My contributions include: 
        1) \textbf{Audio Analysis:} evaluated audio quality using signal-to-noise ratio and visualize the results.
        2) \textbf{Transcription Processing:} applied forced alignment to get the timestamps of the human generated transcriptions.
        3) \textbf{Acoustic and Language Model Training:} used Kaldi nnet3 to train an acoustic model with for 40 hours of children's speech and use Librispeech corpus to train the language model.
        4) \textbf{Toolkits Comparison:} compared word-error-rate (WER) of the existing open-source speech recognition toolkits on children speech corpus including Kaldi and CMU Sphinx.
        5) \textbf{Model Improvement:} applied speaker adaptation, vocal tract length normalization (VTLN) to improve the existing models.
    \end{Detail}
    
    \Gap
    \Entry
    \textbf{Spoken Language Assessment for ESL Learner | NCSU} \hfill Sept 2018 - Present (Ongoing  Project)
    \begin{Detail}
        \BulletItem
        Aimed at building an automatic spoken language assessment system based on the grammatical and semantical correctness of speech responses.
        \BulletItem
        My contributions include: 
        1) trained an ASR engine with 9,000+ utterances from ESL learners along with 1,000+ hours external speech.
        2) applied pitch normalization and speech adaptation techniques to reduce differences between different models.
        3) trained a supervised neural network classifier on the output transcription for response quality assessment.
    \end{Detail}
    
    % \Entry
    % \Gap
    % \textbf{Electronic Medical Record (EMR) System Development | WKU } \hfill
    % \DatestampYM{2016}{01} --
    % \DatestampYM{2016}{10}
    
    % \begin{Detail}
    % \BulletItem
    % Assisted research advisor with composing the research proposal and applying for funding
    % \BulletItem
    % Analyzed the usage of EMR system in Chinese small-scale clinics
    % \BulletItem
    % Evaluated the efficacy of a frequent set mining algorithm in retrieving clinical record data
    % \end{Detail}
    \Gap
    \Entry
    \textbf{Social Intervention for Children with Autism Spectrum Disorder (ASD) | WKU } \hfill \DatestampYM{2015}{04} --\DatestampYM{2016}{06}
    \begin{Detail}
        \BulletItem
        Aimed at building an educational game for children with ASR and also increase the awareness of the ASD.
        \BulletItem
        My contributions include: 1) conducted background research on accessibility of Technology-Based Intervention (TBI) for Chinese children with ASD.
        2) designed the website of WKU Autism Network.
        3) composed and edited the research booklet: Autism Advocate to increase people's understanding of ASD.
        4) programmed a Leap Motion touchless drawing application for social skill intervention.
    \end{Detail}
    
    % %%%%%%%%%%%%%%%%%%
    % %% PUBLICATIONS %%
    % %%%%%%%%%%%%%%%%%%
    
    % \Section
    % {Publications}
    % {Publications}
    % {PDF:Publications}
    
    % % Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
    % \begingroup
    % \renewcommand{\MaxNumberedItem}{[8888]}
    
    % \Gap
    % \BulletItem{Lijun Pan*, \underline{Xiaoting Fu*}, Fangfang Cai, Yu Meng, Changjiang Zhang,
    % ``A Compact Electronic Medical Record System for Regional Clinics and Health Centers in China: Design and Its Application,''
    % in \textit{Proceedings of 2016 IEEE International Conference on Bioinformatics and Biomedicine (BIBM)},
    % Shenzhen, Guangdong, China,
    % \DatestampYM{2016}{12}.} (pp. 1015-1020). (* co-first authorship)
    
    % \Gap
    
    % \BulletItem{Lijun Pan*, \underline{Xiaoting Fu*}, Fangfang Cai, Yu Meng, Changjiang Zhang,
    % ``Design a Novel Electronic Medical Record System for Regional Clinics and Health Centers in China,''
    % in \textit{In Proceedings of 2016 2nd IEEE International Conference on Computer and Communications (ICCC)},
    % Chengdu, Sichuan, China,
    % \DatestampYM{2016}{10}.}(pp. 38-41). (* co-first authorship)
    
    % \endgroup
    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% AWARDS & SCHOLARSHIPS %%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \Section
    {Awards \&\newline
    Activities}
    {Awards \& Activities }
    {PDF:AwardsAndScholarships}
    
    \BulletItem
    Outstanding University Graduate, Zhejiang Province
    \hfill
    \DatestampY{2017}
    \BulletItem
    Dean's List,
    Fall 2013 through Spring 2017,
    College of Natural Science
    \hfill
    \DatestampY{2013} --
    \DatestampY{2017}
    
    \Gap
    \BulletItem
    Microsoft Kinect Hackathon,
    Third Class, Microsoft, Beijing, China
    \hfill
    \DatestampY{2014}
    
    \end{Body}
    \end{document}
    
    